---
title: "covid"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Visualize the spread of the virus by creating
a heatmap of the density of confirmed cases.

We need to install Packages:

Getting Data ready:

```{r}
library(tidyverse)
library(readr)
library(dplyr)
library(mapdata)
library(usmap)
library(ggplot2)
library(gganimate)

Data_1 = "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"

Global_Confirm <- read_csv(url(Data_1))
#view(Global_Confirm)

Data_2 = "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"

Global_Death <- read_csv(url(Data_2))
#view(Global_Death)

Data_3 = "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_recovered_global.csv"

Global_Recovered <- read_csv(url(Data_3))
#view(Global_Recovered)

Data_4 = "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_US.csv"

US_Confirm <- read_csv(url(Data_4))
#view(US_Confirm)

Data_5 = "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_US.csv"

US_Death <- read_csv(url(Data_5))
#view(US_Death)
```

We use the readr package to read the csv file each time it gets updated.
This should give us the most up to date data.

Discovering Data:
```{r}
head(Global_Confirm)
head(Global_Death)
head(Global_Recovered)
head(US_Confirm)
head(US_Death)
```

Maniupulating Data
```{r}
d1 <- US_Confirm[,-c(0:6,8:11)]
head(d1)
dim(d1)

d2 <- d1 %>% 
  gather(-Province_State, key="Day",value = "cases") %>% 
  group_by(Province_State, Day) %>% 
  select(Province_State,Day,cases) %>% 
  summarise(cases=sum(cases))

d2 %>% 
  ggplot(aes(x=Day, y=Province_State, fill=cases)) +
  geom_raster()

```

Creating States
```{r}
d2$cases

d2 <- rename(d2, state = Province_State)
head(statepop)


d3 <- d2 %>% 
  filter(state == "Minnesota")


## Creating Dates

d3$Day <-str_replace_all(d3$Day, c("/"), ".")
d3

d4 <- d3 %>% 
  mutate(Day=as.Date(Day, format = "%m.%d.%y"))
d4

a1<-data.frame("id"=c(1), "date"=c("1.22.20"))
head(a1)
a1$date<-format(as.Date(a1$date), "%d.%m.%y")

## Creating Map
plot_usmap(
    data = d4, values = "cases", include = c("Minnesota"), color = "red"
  ) + 
  scale_fill_continuous(
    low = "white", high = "red", name = "Population (2015)", label = scales::comma
  ) + 
  labs(title = "Western US States", subtitle = "These are the states in the Pacific Timezone.") +
  theme(legend.position = "right") +
  transition_time(Day) +
  labs(title = "Year: {frame_time}")

d4 %>% 
  ggplot(aes(x=state, y=cases))+
  geom_bar(stat = "identity") +
  transition_time(Day)

?transition_time

```

Creating a Barchart that shows the top 10 states infected. Alongside the deaths

```{r}
## Data Filtering

b_confirm_1 <- US_Confirm[,-c(2:6,8:11)]
b_death_1 <- US_Death[,-c(2:6,8:11)]

dim(US_Confirm)
dim(US_Death)

head(b_confirm_1)
head(b_death_1)

b_confirm_2 <- b_confirm_1 %>%
  gather(-Province_State,-UID,key="Day",value="infected_cases") %>% 
  mutate(Day=as.Date(Day, format = "%m/%d/%y")) %>% 

b_death_2 <- b_death_1 %>%
  gather(-Province_State,-UID,key="Day",value="death_cases") %>% 
  mutate(Day=as.Date(Day, format = "%m/%d/%y"))

## Joining two tables
b_joined <- b_death_2 %>% 
  left_join(b_confirm_2,by=c("UID","Day","Province_State"))

## Getting top 10 infected states
b_joined %>% 
  filter(Day == "2020-05-01") %>% 
  top_n(10)







```